% Cover letter using letter.cls
\documentclass[10pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\newcommand{\companyname}{CyraCom International}

\begin{document}

\signature{Nan "Leon" Li}                  % name for signature 
\longindentation=5pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{\companyname} 

\begin{center}
\large\bf Nan "Leon" Li \\
2600 E. SPRINGFIELD PL UNIT 29 \\ Chandler, AZ 85286 \\ (480) 246-6540%(480) 277-5053
\end{center} 
%\vfill % forces letterhead to top of page

\opening{Dear Hiring Manager:} 

\noindent On Indeed.com Roberto Ayala referred me to the position Mandarin Bi-Lingual interpreter. With my previous experience as a programmer I would be adept at communicating and presenting information in a concise and verfiably correct manner. I work hard to be part of the team, always striving to resolve issues and improve existing processes. I have shipped multiple products to customer under deadlines. I am also a fast learner--I love to learn and process new things. 

\noindent In the past I was an experienced software developer in web/mobile gaming, shipping multiple games as part of a team alongside designers, artists, and mathematicians. I'm knowlegeable and versed at the technical aspects of 2D and 3D content-creation with experience in Photoshop and Blender. I have software development experience on various projects in networking, front-end/GUI development, 3D graphics, and back-end development. 

\noindent Thank you very much for going over my resume and considering me for this position. I hope we can arrange a meeting for further in-depth discussions. I can be reached at 480-246-6540.

\closing{Sincerely yours,}

\signature{}
 
\encl{}  				% Enclosures

\end{letter}
 

\end{document}




